Digital History in Finland, 1488-1828

### 2016-06-22 inst/examples/manuscript-krakow.Rmd
Rmd update

Erityisesti:

Riksdag Stockholm 20 januari 1719 1 juni 1719

Riksdag Stockholm 14 maj 1734 14 december 1734

Riksdag Stockholm 21 februari 1765 21 oktober 1766

Riksdag Norrköping & Stockholm 22 april 1769 5 februari 1770

Riksdag Stockholm 19 juni 1771 12 september 1772

Riksdag Gävle 26 januari 1792 24 februari 1792

--> tapahtuuko Gävlessä selvää nousua julkaisemisessa.

@@

```{r valtiopaivat-total, echo=FALSE, warning=FALSE, fig.width=11, fig.height=4}
# Use timeinterval year intervals
dfsel = df0
#dfsel = subset(df0, publication_place == "Stockholm")
#dfsel = subset(df0, publication_place == "Norrköping")
#dfsel = subset(df0, publication_place == "Gävle")

@@

# Draw Figure
theme_set(theme_bw(20))
p <- ggplot()
p <- p + geom_rect(data = rectangles, 
	   aes(xmin=xmin, xmax=xmax, ymin=ymin, ymax=ymax, fill=shade), alpha=0.8) + 
         scale_fill_manual(values = cols) # + guides(fill = "none") 
p <- p + geom_line(data = dfm, aes(x = date, y = Documents), col = "black")
p <- p + geom_point(data = dfm, aes(x = date, y = Documents), col = "black")
p <- p + scale_x_continuous(breaks=seq(min(dfm$date), max(dfm$date), 20))
p <- p + ggtitle("Publishing activity")
p <- p + ylab("Documents / Year")
p <- p + xlab("Year")
p <- p + ggtitle("Riksdagar - overall titlecount (Fen + Kun)")
print(p)
```

```{r valtiopaivat-gavle, echo=FALSE, warning=FALSE, fig.width=11, fig.height=4}
# Use timeinterval year intervals
myplace = "Gävle" # Norrköping / Stockholm
dfsel = subset(df0, publication_place == myplace)
minyear = 1700
maxyear = 1800

df <- subset(dfsel, publication_year >= minyear & publication_year < maxyear)

@@

rect_left <- c(min(na.omit(dfm$date)),
               1719-.5, 1719+.5, # Stockholm 20 januari 1719 1 juni 1719
               1734-.5, 1734+.5, # Stockholm 14 maj 1734 14 december 1734
               1765-.5, 1766+.5, # Stockholm 21 februari 1765 21 oktober 1766
               1769-.5, 1770+.5, # Norrköping & Stockholm 22 april 1769 5 februari 1770
               1771-.5, 1772+.5, # Stockholm 19 juni 1771 12 september 1772
               1792-.5, 1792+.5, # Gävle 26 januari 1792 24 februari 1792	       
               max(na.omit(dfm$date)))
  rectangles <- data.frame(
    xmin = rect_left[-length(rect_left)],
    xmax = rect_left[-1],
    #xmin = min(dfsel$publication_year),
    #xmax = max(dfsel$publication_year),    
    ymin = ymin,
    ymax = ymax
    )
  rectangles$shade <- rep(c("White", "Highlight"), length = nrow(rectangles))
  #rectangles$shade <- rep(c("White", "Highlight"), length = nrow(rectangles))

@@

# Draw Figure
theme_set(theme_bw(20))
p <- ggplot()
p <- p + geom_rect(data = rectangles, 
	   aes(xmin=xmin, xmax=xmax, ymin=ymin, ymax=ymax, fill=shade), alpha=0.8) + 
         scale_fill_manual(values = cols) # + guides(fill = "none") 
p <- p + geom_line(data = dfm, aes(x = date, y = Documents), col = "black")
p <- p + geom_point(data = dfm, aes(x = date, y = Documents), col = "black")
p <- p + scale_x_continuous(breaks=seq(minyear, maxyear, 20))
p <- p + ggtitle("Publishing activity")
p <- p + ylab("Documents / Year")
p <- p + xlab("Year")
p <- p + ggtitle(paste("Riksdagar - titlecount in ", myplace, sep = ""))
print(p)

>>>>

In particular: Riksdag Stockholm 20 januari 1719 1 juni 1719; Stockholm 14 maj 1734 14 december 1734; Stockholm 21 februari 1765 21 oktober 1766; Norrköping & Stockholm 22 april 1769 5 februari 1770; Stockholm 19 juni 1771 12 september 1772; Gävle 26 januari 1792 24 februari 1792.

@@

```{r riksdar1, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=7, fig.show="hold", out.width="430px"}
for (catal in as.character(unique(df0$catalog))) {

  # Use timeinterval year intervals
  dfsel = subset(df0, catalog == catal)
  #dfsel = subset(df0, publication_place == "Stockholm")
  #dfsel = subset(df0, publication_place == "Norrköping")
  #dfsel = subset(df0, publication_place == "Gävle")

@@

  # Draw Figure
  theme_set(theme_bw(20))
  p <- ggplot()
  p <- p + geom_rect(data = rectangles, 
	   aes(xmin=xmin, xmax=xmax, ymin=ymin, ymax=ymax, fill=shade), alpha=0.8) + 
         scale_fill_manual(values = cols) # + guides(fill = "none") 
  p <- p + geom_line(data = dfm, aes(x = date, y = Documents), col = "black")
  p <- p + geom_point(data = dfm, aes(x = date, y = Documents), col = "black")
  p <- p + scale_x_continuous(breaks=seq(min(dfm$date), max(dfm$date), 20))
  p <- p + ggtitle("Publishing activity")
  p <- p + ylab("Documents / Year")
  p <- p + xlab("Year")
  p <- p + ggtitle(catal)
  print(p)
}
```

Focus on Gävle (gray) during riksdagar. Gävle has `r sum("Gävle" %in% fen$publication_place)` occurrences in Fennica, hence not included here. The figure on Gävle is based on Kungliga.

```{r riksdar2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=7, out.width="430px"}

  # Use timeinterval year intervals
  myplace = "Gävle" # Norrköping / Stockholm
  minyear = 1700
  maxyear = 1800
  catal = "Kungliga"

  df = subset(df0, publication_place == myplace & catalog == catal)
  df <- subset(df, publication_year >= minyear & publication_year < maxyear)

@@

  rect_left <- c(min(na.omit(dfm$date)),
               1719-.5, 1719+.5, # Stockholm 20 januari 1719 1 juni 1719
               1734-.5, 1734+.5, # Stockholm 14 maj 1734 14 december 1734
               1765-.5, 1766+.5, # Stockholm 21 februari 1765 21 oktober 1766
               1769-.5, 1770+.5, # Norrköping & Stockholm 22 april 1769 5 februari 1770
               1771-.5, 1772+.5, # Stockholm 19 juni 1771 12 september 1772
               1792-.5, 1792+.5, # Gävle 26 januari 1792 24 februari 1792	       
               max(na.omit(dfm$date)))
  rectangles <- data.frame(
    xmin = rect_left[-length(rect_left)],
    xmax = rect_left[-1],
    ymin = ymin,
    ymax = ymax
    )
  rectangles$shade <- rep(c("White", "Highlight"), length = nrow(rectangles))

@@

  # Draw Figure
  theme_set(theme_bw(20))
  p <- ggplot()
  p <- p + geom_rect(data = rectangles, 
	   aes(xmin=xmin, xmax=xmax,
	       ymin=ymin, ymax=ymax,
	       fill=shade), alpha=0.8) + 
         scale_fill_manual(values = cols) # + guides(fill = "none") 
  p <- p + geom_line(data = dfm, aes(x = date, y = Documents), col = "black")
  p <- p + geom_point(data = dfm, aes(x = date, y = Documents), col = "black")
  p <- p + scale_x_continuous(breaks = seq(minyear, maxyear, 20))
  p <- p + ggtitle("Publishing activity")
  p <- p + ylab("Documents / Year")
  p <- p + xlab("Year")
  p <- p + ggtitle(paste(myplace, " (", catal, ")", sep = ""))
  print(p)
